*Supplementary Material 1*

### 2022-02-23 ms/si.Rmd
Update MS

---
title: "*Supplementary Material 1*"
subtitle: "Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
---

---
bibliography: 
- `r here::here("ms/si_references.yaml")`
- `r here::here("ms/si_references_other.yaml")`
- `r here::here("ms/si_references_other.yaml")`
- `r here::here("ms/si_fossils.bib")`
---

@@

```{r join-by, results = "markup"}
# Make table showing method of joining accessions across loci
sanger_accessions_selection %>% 
    # Remove outgroup and plastome species
  anti_join(
    unique(select(plastome_seqs_combined_filtered, species)),
    by = "species") %>%
  left_join(select(sanger_sampling, species, outgroup), by = "species") %>%
  # FIXME why is this NA?
  # filter(is.na(outgroup)) %>%
  filter(outgroup == FALSE) %>%
  select(-outgroup) %>%
  assert(not_na, join_by, species) %>%
  assert(is_uniq, species) %>%
  tabyl(join_by) %>%
  arrange(n) %>%
  adorn_totals() %>%
  mutate(
    join_by = str_to_sentence(join_by) %>%
      str_replace_all("Monophy", "Monophyletic"),
    n = number(n),
    percent = case_when(
      join_by != "Total" ~ percent(percent),
      TRUE ~ ""
    )
  ) %>%
  rename(
    "Method" = join_by,
    `%` = percent) %>%
  flextable() %>%
  italic(1,2, part = "header") %>%
  autofit()
```

>>>>

---
title: "*Supplementary Material 1*"
subtitle: "Tables and Figures"
mainfont: Roboto-Regular.ttf
fontsize: 11pt
mainfontoptions: 
  - BoldFont=Roboto-Bold.ttf
  - ItalicFont=Roboto-Italic.ttf
  - BoldItalicFont=Roboto-BoldItalic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: default
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "frontiers.csl"]
  bookdown::word_document2:
    pandoc_args: [ "--csl", "frontiers.csl"]
    toc: no
    number_sections: no
    reference_docx: Frontiers_Template_SI.docx
header-includes: 
  - \usepackage{float} # keep figures from floating away
  - \usepackage{booktabs} # need for kable tables
  - \usepackage{colortbl} # need for kable tables
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # keep figures from floating away
  - \usepackage{fancyhdr} # enable header
  - \pagestyle{fancy}  # enable header
  - \fancypagestyle{plain}{\pagestyle{fancy}} # show header on first page
  - \renewcommand{\headrulewidth}{0pt} # delete line beneath header
  - \fancyhead[RE,RO]{Supplementary Material} # add header on right side
  - \fancyhead[LO,LE]{} # suppress automatic section header on left side
  - \setlength{\headheight}{13.6pt}
  - \cfoot{\thepage} # footer
editor_options: 
  chunk_output_type: console
params:
  doc_type: manual
nocite: '@*'
---

---
bibliography: 
- `r here::here("ms/si_references.yaml")`
- `r here::here("ms/si_references_other.yaml")`
---

@@

```{r join-by, results = "markup"}
# Make table showing method of joining accessions across loci
sanger_accessions_selection %>% 
  # Remove outgroup and plastome species
  anti_join(
    unique(select(plastome_seqs_combined_filtered, species)),
    by = "species") %>%
  assert(not_na, join_by, species) %>%
  assert(is_uniq, species) %>%
  tabyl(join_by) %>%
  arrange(n) %>%
  adorn_totals() %>%
  mutate(
    join_by = str_to_sentence(join_by) %>%
      str_replace_all("Monophy", "Monophyletic"),
    n = number(n),
    percent = case_when(
      join_by != "Total" ~ percent(percent),
      TRUE ~ ""
    )
  ) %>%
  rename(
    "Method" = join_by,
    `%` = percent) %>%
  flextable() %>%
  italic(1,2, part = "header") %>%
  autofit()
```
